Guarded Recursion in Agda via Sized Types

### 2019-02-01 code-oneclock-paper/latex/paper.tex
trying to cut
text changes

This work can be extended is several different directions.

Various type theories for guarded recursion in the literature include
dependent types. Currently, there exist two disciplines for mixing
dependent types with guarded recursion: delayed substitutions
\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. We plan to extend
the syntax and semantics of \GTT\ with dependent types following one
of these two disciplines.

Abel and Vezzosi \cite{AbelV14} formalized a simple type theory
extended with the later modality in Agda. They focus on operational
properties of the calculus and give a certified proof of strong
normalization. In future work, we plan to investigate the metatheory
and the dynamic behaviour of \GTT, for example by formalizing a  type
checker and a normalization algorithm.

@@

Finally, we want to understand weather it is possible to reduce sized types to guarded
recursion.  This does not seems directly doable, since sizes are not uniquely employed with coinductive types as a
tool for easing the productivity check of corecursive
definitions, but they are also used as auxiliary arguments of inductive
types for facilitating the termination check of recursive
definitions. It seems that the existing type theories for guarded
recursion are not capable of capturing this dual aspect of sizes.

%%
%% Bibliography
%%

>>>>

This work can be extended is several different directions.
Various type theories for guarded recursion in the literature include
dependent types. Currently, there exist two disciplines for mixing
dependent types with guarded recursion: delayed substitutions
\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
the syntax and semantics of \GTT\ with dependent types following one
of these methods.

Abel and Vezzosi \cite{AbelV14} formalized a simple type theory
extended with the later modality in Agda. They focus on operational
properties of the calculus and give a certified proof of strong
normalization. As future work, we plan to investigate the metatheory
and the dynamic behaviour of \GTT\ by formalizing a  type
checker and a normalization algorithm.

@@

Finally, we want to understand weather it is possible to reduce sized
types to guarded recursion.  This does not seems directly doable,
since sizes are not uniquely employed with coinductive types as a tool
for easing the productivity check of corecursive definitions, but they
are also used as auxiliary arguments of inductive types for
facilitating the termination check of recursive definitions. It seems
that, in order to capture this dual aspect of sizes, one needs to
extend the existing type theories for guarded recursion with
additional features.
%%
%% Bibliography
%%
